```{r, echo=FALSE, purl=FALSE, message=FALSE}
knitr::opts_chunk$set(echo=FALSE, comment = "#>")

library(stringr)
library(dplyr)
library(ggplot2)
library(knitr)
library(kableExtra)

filenames <- list.files("thumbs/") %>% str_remove("thumb_")
c_gviz_sub <- read.csv("../../API_tests/catal_sample_1000_GV_output.csv") %>%   # read peter's data here 
    filter(filename %in% filenames) # keep only subset of 766 we actually have thumbnail images of
```

# Some generic introspection

Three types of results from Google Vision API:

- `label` detect broad sets of objects based
- `entity` uses Google Image Search to find topical entities 
- `ocr` for Optical Character Recognition of text

`entity` and `label` receive a `score` as a measure for how confident Google is about this.

## Frequency of labels 

```{r}
ggplot(c_gviz_sub, aes(type)) + geom_bar()
```

## Distribution of probablity scores

Mean score overall: `r mean(c_gviz_sub$score, na.rm = T)`. 

```{r, warning=FALSE, fig.height=4}
c_gviz_sub %>% 
  filter(type != 'ocr') %>% 
  ggplot(aes(score)) + 
    geom_bar() +
    #geom_vline(aes(xintercept = mean(score, na.rm = T)), color = "orange") + 
    facet_wrap(~type, nrow = 2)
```


## Top ranking labels

Number of lables with mean score of .8 or higher:

```{r}
c_gviz_sub %>% 
  group_by(type, value) %>% 
  summarise(mean_score = mean(score, na.rm = T)) %>% # this eliminates 'ocr' which has NA score 
  filter(mean_score >= .8) %>% 
  tally() %>% 
  kable()
```


## Score distribution for those top ranking labels

NOTE: There can be labels that are only mentioned very rarely, but scored high. Ns added to the plots. 

```{r, fig.height=8}
# get top lables 
top_labels <- c_gviz_sub %>% 
  group_by(type, value) %>% 
  summarise(mean_score = mean(score, na.rm = T),
            N = n()) %>% # this eliminates 'ocr' which has NA score 
  filter(mean_score >= .8) 

# plot for entity
c_gviz_sub %>% 
  filter(value %in% top_labels$value,
         type == "entity") %>% 
  left_join(top_labels, by = "value")  %>% 
  ggplot(aes(x=reorder(value, N), y=score, label = N)) + 
    geom_boxplot() +
    geom_text(aes(y = .22)) +
    coord_flip() +
    ggtitle("entities with scores of .8 or higher") +
    xlab("")

# plot for label
c_gviz_sub %>% 
  filter(value %in% top_labels$value,
         type == "label") %>% 
  left_join(top_labels, by = "value")  %>% 
  ggplot(aes(x=reorder(value, N), y=score, label = N)) + 
    geom_boxplot() +
    geom_text(aes(y = .6)) +
    coord_flip() +
    ggtitle("labels with scores of .8 or higher") +
    xlab("")
```


## Most used labels (more than 50 times) and their mean scores

```{r}
c_gviz_sub %>% 
  filter(type != 'ocr') %>% 
  group_by(type, value) %>% 
  summarize(N = n(),
            mean_score = mean(score, na.rm = T)) %>% 
  filter(N > 50) %>% 
  arrange(desc(N)) %>% 
  kable()
 
```


## Highest scoring labels (over 0.8) and their frequency

```{r}
c_gviz_sub %>% 
  filter(score > 0.8, type == "label") %>% 
  #group_by(type, value) %>% 
  count(value) %>% 
  arrange(desc(n)) %>% 
  kable(caption = "Label")

c_gviz_sub %>% 
  filter(score > 0.8, type == "entity") %>% 
  #group_by(type, value) %>% 
  count(value) %>% 
  arrange(desc(n)) %>% 
  kable(caption = "Entity")
```

