```{r, echo=FALSE, purl=FALSE, message=FALSE}
knitr::opts_chunk$set(echo=FALSE, comment = "#>")

library(stringr)
library(dplyr)
library(tidyr)
library(ggplot2)
library(knitr)
library(kableExtra)

filenames <- list.files("thumbs/") %>% str_remove("thumb_")
c_gviz_sub <- read.csv("../../API_tests/catal_sample_1000_GV_output.csv") %>%   # read peter's data here 
    filter(filename %in% filenames) # keep only subset of 766 we actually have thumbnail images of
clf <- read.csv("../../API_tests/catal_sample_Clarifi_predictions.csv")

tdf <- clf %>% 
  rename(score = value,         # renaming 
         value = name,
         filename = file_name) %>%
  mutate(type = "CP_label",     # add type: CP_label
         score = round(score, 2)) %>% # reduce to 2 digits
  select(type, value, score, filename)

preds <- c_gviz_sub %>% # combine for summary stats below
  mutate(type = as.character(type), # renaming
         type = ifelse(type == "entity", "GV_entity", (ifelse(type == "label", "GV_label", "GV_ocr")))) %>% 
  select(type, value, score, filename) %>% 
  rbind(tdf)

# join the labels to check for agreement
dfr <- preds %>% 
  filter(type %in% c("CP_label", "GV_label")) %>% 
  group_by(filename, value) %>%
  tally() %>% 
  filter(n > 1) %>% # these are images that have the same label twice
  left_join(preds, by = c("filename", "value"))

```

# Some general introspection

Three types of results from Google Vision API:

- `GV_label` broad sets of objects (with probabilities)
- `GV_entity` uses Google Image Search to find topical entities  (with probablities)
- `GV_ocr` for Optical Character Recognition of text

`GV_entity` and `GV_label` receive a `score` as a measure for how confident Google is about this.


One type of results from Clarifai Predict API:

- `CP_label` "concepts with corresponding probabilities of how likely it is these concepts are contained within the image"


## Frequency of all labels

```{r, fig.height=2}
ggplot(preds, aes(type)) + geom_bar()
```

## Frequency of unique labels

```{r, fig.height=2}
preds %>% 
  group_by(type) %>% 
  summarise(ndist = n_distinct(value)) %>% 
  ggplot(aes(type, ndist)) + geom_col()
```


## Distribution of scores

Range of scores:

- GV entity: `r range(c_gviz_sub$score[which (c_gviz_sub$type == "entity")])`
- GV label: `r range(c_gviz_sub$score[which (c_gviz_sub$type == "label")])`
- CP name: `r range(clf$value)`



```{r, warning=FALSE, fig.height=6}

# add cfl$type in and rename
preds %>% 
  filter(type != 'GV_ocr') %>% 
  ggplot(aes(score)) + 
    geom_bar() +
    facet_wrap(~type, nrow = 3)
```


## Top ranking labels (on average)

Number of labels with __mean__ score of .8 or higher:

```{r}
preds %>% 
  group_by(type, value) %>% 
  summarise(mean_score = mean(score, na.rm = T)) %>% # this eliminates 'ocr' which has NA score 
  filter(mean_score >= .8) %>% 
  tally() %>% 
  kable()
```


## Score distribution for those top ranking labels

NOTE: There can be labels that are only mentioned very rarely, but scored high in confidence. Ns added to the plots. 

For Clarifai Preditions [CP] only top labels with mean score of **.95** or higher (N = 31).

```{r, fig.height=8}
# get top lables 
top_labels <- c_gviz_sub %>% 
  group_by(type, value) %>% 
  summarise(mean_score = mean(score, na.rm = T),
            N = n()) %>% # this eliminates 'ocr' which has NA score 
  filter(mean_score >= .8) 

# plot for entity
c_gviz_sub %>% 
  filter(value %in% top_labels$value,
         type == "entity") %>% 
  left_join(top_labels, by = "value")  %>% 
  ggplot(aes(x=reorder(value, N), y=score, label = N)) + 
    geom_boxplot() +
    geom_text(aes(y = .22)) +
    coord_flip() +
    ggtitle("GV entities with scores of .8 or higher") +
    xlab("")

# plot for label
c_gviz_sub %>% 
  filter(value %in% top_labels$value,
         type == "label") %>% 
  left_join(top_labels, by = "value")  %>% 
  ggplot(aes(x=reorder(value, N), y=score, label = N)) + 
    geom_boxplot() +
    geom_text(aes(y = .6)) +
    coord_flip() +
    ggtitle("GV labels with scores of .8 or higher") +
    xlab("")

# plot for Clarifai
clf_top_labels <- clf %>% 
  group_by(name) %>% 
  summarise(mean_score = mean(value),
            N = n()) %>% 
  filter(mean_score >= .95) 

clf %>% 
  filter(name %in% clf_top_labels$name) %>% 
  left_join(clf_top_labels, by = "name")  %>% 
  ggplot(aes(x=reorder(name, N), y=value, label = N)) + 
    geom_boxplot() +
    geom_text(aes(y = .6)) +
    coord_flip() +
    ggtitle("CP labels with scores of .95 or higher") +
    xlab("")
```


## Most used labels (more than 50 times) and their mean scores

```{r}
preds %>% 
  filter(type != 'GV_ocr') %>% 
  group_by(type, value) %>% 
  summarize(N = n(),
            mean_score = mean(score, na.rm = T)) %>% 
  filter(N > 50) %>% 
  arrange(type, desc(N)) %>% 
  kable()
 
```


## Highest scoring labels (GV over 0.8, CP over .95) and their frequency

```{r}
preds %>% 
  filter(score > 0.8, type == "GV_label") %>% 
  count(value) %>% 
  arrange(desc(n)) %>% 
  kable(caption = "GV Label")

preds %>% 
  filter(score > 0.8, type == "GV_entity") %>% 
  count(value) %>% 
  arrange(desc(n)) %>% 
  kable(caption = "GV Entity")

preds %>% 
  filter(score > 0.95, type == "CP_label") %>% 
  count(value) %>% 
  arrange(desc(n)) %>% 
  kable(caption = "GCP Label")
```

## Labels occuring in both sets: GV and CP

```{r}
preds %>%
  filter(type %in% c("GV_label", "CP_label")) %>% 
  group_by(value, type) %>% 
  tally() %>% 
  spread(type, n) %>%      # spread the above table by type, 
  drop_na() %>%            # only take rows that don't have NAs
  # arrange(desc(GV_label)) %>% 
  kable(caption = "GV AND CP labels")
```

## Predictor "agreement": images

Predicors agree on at least one label in
`r dfr %>% filter(type == "GV_label") %>%  group_by(filename) %>% summarise(nf = n()) %>% nrow()`  out of the total of 766 images.

Broken down by number of agreed labels below.

```{r}

dfr %>% 
  filter(type == "GV_label") %>% # just get rid of one - they are double
  group_by(filename) %>% 
  summarise(nf = n()) %>% 
  ggplot(aes(nf)) + geom_histogram(binwidth = 1) +
     xlab("Number of labels Google and Clarifai agree upon per image") +
     ylab("") +
     scale_x_continuous(breaks=1:9) +
     scale_y_continuous(breaks=seq(0, 200, 20))
```


## Predictor "agreement": scores
Labels used by **CP** _and_ **GV** to describe the _same_ image. Distribution of scores shown for labels that were used on more than 10 images.

```{r}
# make the data frame

vv <- dfr %>% 
  group_by(value, type) %>% 
  tally() %>% 
  filter(nn > 10) %>% pull(value)

dfr %>% 
  filter(value %in% vv) %>% 
  ggplot(aes(value, score, color=type)) + 
    geom_boxplot() + 
    coord_flip()

```

